### 2023-11-26 docs/report/progress/article.tex
chore: project latex doc
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}

\title{Information Retrieval - Report - Project: Art For Sale}

\author{Morales Mariciano Jeferson}
\author{Piloni Filippo}
\affil{Universita' della Svizzera italiana, Faculty of Informatics, Lugano, Switzerland}

\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

\begin{spacing}{1}   % use double spacing for rest of manuscript

\section{Obtained results}
Github code repository: \url{https://github.com/JekxDevil/IR-ArtForSale}\\
For the \textit{Art-For-Sale} project we selected the following websites to collect the data from:
\begin{itemize}
    \setlength\itemsep{0.3em}
    \item [1.] \url{www.artsy.net}
    \item [2.] \url{www.saatchiart.com}
    \item [3.] \url{www.artfinder.com}
\end{itemize}
For each website, a spider to crawl the site was created. 
Website specific pre-fixed tags have been used to choose categories to explore, 
searching content for each of the tag and retrieve categorized grouped results. \\
The crawler explores the pages of the single artworks and gathers from each one the following information:
\begin{itemize}
    \setlength\itemsep{0.3em}
    \item Name of the artwork and author
    \item Url of the image of the artwork
    \item Price
    \item Link to the page
    \item Tags associated to the artwork
    \item Description of the artwork (if present)
\end{itemize}
Results are saved in json files and we are starting the creation of an inverted index combining all the results obtained.\\
In total, we obtained around $\approx9000$ documents to be used in our project\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-0.5cm}\section{Planned results}
The next step will be implementing the \textbf{inverted index} and the \textbf{frontend} and \textbf{backend} part.\\
For the inverse index, documents are indexed based on all the text information, providing a quick access based on 
tags, price and characteristics listed above.\\
We then decided to implement a simple yet highly customizable interface in Vuejs that will allow the user to filter the results 
based on the tags associated to the artworks and showcase all the important information about the artworks obtained thanks to the retrieval model. \\
Our plan is to implement \underline{at least} the following features:
\begin{itemize}
    \setlength\itemsep{0.3em}
    \item Result presentation
    \item Automatic recommendation
\end{itemize}
With these, it would be possible to accomplish our goal, so to create a retrieve system with a good interface 
that returns results based on the user's search history.
\end{spacing}
\end{document}

\subsection{Use of This Document}

This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.  The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it. Authors may use it as a template to create their own manuscript. While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.

\subsection{English}

Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example. In addition, good English usage is essential. Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced. Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}. SPIE authors will receive a 15\% discount off their services. A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission. Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.

\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

\begin{table}[ht]
\caption{Fonts sizes and styles.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline 
\end{tabular}
\end{center}
\end{table}

\section{Parts of Manuscript}

This section describes the normal structure of a manuscript and how each part should be handled. The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.

\subsection{Title and Author Information}
\label{sect:title}
The article title appears left justified at the top of the first page. The title font is 16 pt., bold. The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized. Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.). The word ``novel'' should not appear in the title, as publication will imply novelty. Avoid the use of acronyms in the title, unless they are widely understood.

The list of authors immediately follows the title, 18 points below. The font is 12 pt., bold and the author names are left justified. The author affiliations and addresses follow the names, in 10-pt., normal font and left justified. For multiple affiliations, each affiliation should appear on a separate line. Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations. The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.

\subsection{Abstract}
The abstract should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting journals, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Medical Imaging}. Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}. Helpful guidelines for structured abstracts are available on the website of the journal.

\subsection{Subject terms/Keywords}
Keywords are required. Please provide 3-6 keywords related to your paper.

\subsection{Body of Paper}
The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.

To provide transition elements in your paper, it is important to refer back (or forward) to specific sections. Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out. When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.

At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).

\subsection{Footnotes}
Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided. If absolutely necessary, the footnote mark must come at the end of a sentence. To insert a footnote, use the {\verb|\footnote{}|} command.

\subsection{Appendices}
Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms. Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.

\subsection{Disclosures}
Conflicts of interest should be declared under a separate header. If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest. For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}

\subsection{Code, Data, and Materials Availability}
In support of open scientific exchange, SPIE journals require Data and Code Availability Statements in all accepted papers. This requirement went into effect on 1 May 2023. These statements should describe how to access any data that would be required to replicate or interpret the findings reported in the paper.

\subsection{Acknowledgments}
Acknowledgments and funding information should be added after the conclusion, and before references. Include grant numbers and the full name of the funding body. The acknowledgments section does not have a section number.

\subsection{References}
The References section lists books, articles, and reports that are cited in the paper. This section does not have a section number. The references are numbered in the order in which they are cited. Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.  Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

The references are numbered in the order of their first citation. Citations to the references are made using superscripts, as demonstrated in the preceding paragraph. One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them. Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.

\subsubsection{Reference linking and DOIs}
A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet. The use of DOIs allows readers to easily access cited articles. Authors should include the DOI at the end of each reference in brackets if a DOI is available. See examples at the end of this manuscript. A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}. The inclusion of DOIs will facilitate reference linking and is highly recommended.

In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}. The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.

\subsection{Biographies}
A brief professional biography of approximately 75 words may be provided for each author, if available. Biographies should be placed at the end of the paper, after the references. Personal information such as hobbies or birthplace/birthdate should not be included. Author photographs are not published.

\section{Section Formatting}
\label{sect:sections}
In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections. Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references. (Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.

Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style. The same goes for leading paragraphs of subsections and sub-subsections. Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation. There is no additional space between paragraphs. In LaTeX, paragraphs are separated by blank lines in the source file. Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

\subsection{Subsection Headings}
All important words in a subsection (level 1) header are capitalized. Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end. The heading is left justified and its font is 12 pt. italic.

\subsubsection{Sub-subsection headings}
The first word of a sub-subsection is capitalized. The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known). The heading is left justified and its font is 11 pt. italic.

\section{Figures and Tables}

\subsection{Figures}

Figures are numbered in the order in which they are called out in the text. They should appear in the document in numerical order and as close as possible to their first reference in the text. It may be necessary to move figures or tables around to enhance readability. LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.

Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered. Figure captions are centered below the figure or graph. Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt. font. See Fig.~\ref{fig:example} for an example.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{mcr3b.eps}
\end{tabular}
\end{center}
\caption 
{ \label{fig:example}
Example of a figure caption. } 
\end{figure}

Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
\\
(a) \hspace{5.1cm} (b)
\end{tabular}
\end{center}
\caption 
{ \label{fig:example2}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
\end{figure}

\subsection{Tables}
Tables are numbered in the order in which they are referenced. They should appear in the document in numerical order and as close as possible to their first reference in the text. It is preferable to have tables appear at the top or bottom of the page, if possible. Table captions are handled identically to those for figures, except that they appear above the table. See Table~\ref{tab:fonts} for an example.

\subsection{Video}
Acceptable file formats, including MOV (.mov), MPEG (.mpg), and MP4 (.mp4), are playable using standard media players, such as VLC or Windows Media Player. The recommended maximum size for each video file is 10-12 MB. Authors may insert a representative still image from the video file in the manuscript as a figure. The caption label will be linked by the publisher to the actual video file. The video may also be mentioned in an existing figure caption. Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.  The video number, file type, and file size should be included in parentheses at the end of the figure caption. See Figure \ref{vid:satellite} for an example.

\begin{video}
\begin{center}
{\includegraphics[height=5cm]{satellite.eps}}
\\
\end{center}
\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
\end{video}

\appendix    % this command starts appendixes

\section{Miscellaneous Formatting Details}
\label{sect:misc}
At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.

\subsection{Formatting Equations}
Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the field of view is
\begin{equation}
\label{eq:fov}
2 a = \frac{(b + 1)}{3c} \, ,
\end{equation}
where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma appears after the equation because the next line is a subordinate clause. If the equation ends the sentence, a period should follow the equation. The line following an equation should not be indented unless it is meant to start a new paragraph. Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise. Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..

\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.  The text of the theorem continues on the same line in normal, 10-pt. font, achieved in LaTeX using \verb|\footnotesize|.  For example,

\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}

% \disclosures 
\subsection*{Disclosures}
Conflicts of interest should be declared under a "Disclosures" header. If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.

\subsection* {Code, Data, and Materials Availability} 
In support of open scientific exchange, SPIE journals require Code, Data, and Materials Availability Statements in all accepted papers. This requirement went into effect on 1 May 2023. These statements should describe how to access any data that would be required to replicate or interpret the findings reported in the paper. Authors are encouraged to make the data and code related to the manuscript publicly available whenever possible, and utilize repositories that are well-known to the field (FigShare, Github, CodeOcean, etc.). If the data or code cannot be made publicly available, the authors should state the reason and explain how it can be obtained. Likewise, if data sharing is not applicable, the statement must say so. Example statements may be found in the Author Guidelines for the journal.

\subsection* {Acknowledgments}
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%% References %%%%%

\bibliography{report}   % bibliography data in report.bib
\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst

%%%%% Biographies of authors %%%%%

\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.

\listoffigures
\listoftables

\end{spacing}
\end{document}

### 2023-11-26 frontend/src/stores/document.ts
feat: integration
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@ -10,9 +10,9 @@ export const useDocumentStore = defineStore({
         hasFields: (state) => state.documents.length > 0,
     },
     actions: {
-        async getDocuments(query) {
+        async getDocuments(query: string) {
             try {
-                const response = await axios.get("/api/search/get-documents/", { params: { query } });
+                const response = await axios.get(`http://localhost:8000/api/documents/get-documents/${query}/`);
                 this.documents = response.data.documents;
             } catch (error) {
                 console.error("Error fetching fields:", error);

### 2023-11-26 frontend/vite.config.ts

@@ -12,7 +12,7 @@ export default defineConfig({
                 // search up for workspace root
                 searchForWorkspaceRoot(process.cwd()),
                 // custom rules
-                '/home/filippo/node_modules/primeicons/fonts/'
+                '~/node_modules/primeicons/fonts/'
             ],
         },
     },

### 2023-11-26 Pyterrier example/pyterrier.py
chore: deletion
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@ -1,24 +1,0 @@
-import pyterrier as pt
-import pandas as pd
-if not pt.started():
-    pt.init()
-
-docs_df = pd.DataFrame([
-        ["d1", "this is the first document of many documents"],
-        ["d2", "this is another document"],
-        ["d3", "the topic of this document is unknown"]
-    ], columns=["docno", "text"])
-
-docs_df = pd.DataFrame([
-        ["d1", "the bright blue butterfly hangs on the breeze"],
-        ["d2", "it is best to forget the great sky and to retire from every wind"],
-        ["d3", "under blue sky in bright sunlight one need not search around"]
-    ], columns=["docno", "text"])
-
-docs_df
-
-indexer = pt.DFIndexer("./index_3docs", overwrite=True)
-index_ref = indexer.index(docs_df["text"], docs_df["docno"])
-index_ref.toString()
-
-index = pt.IndexFactory.of(index_ref)

### 2023-11-26 examples/ex-pyterrier.py

@@ -1,36 +1,0 @@
-import pyterrier as pt
-import pandas as pd
-
-
-def run():
-    if not pt.started():
-        pt.init()
-
-    docs_df = pd.DataFrame(
-        [
-            ["d1", "this is the first document of many documents"],
-            ["d2", "this is another document"],
-            ["d3", "the topic of this document is unknown"],
-        ],
-        columns=["docno", "text"],
-    )
-
-    docs_df = pd.DataFrame(
-        [
-            ["d1", "the bright blue butterfly hangs on the breeze"],
-            ["d2", "it is best to forget the great sky and to retire from every wind"],
-            ["d3", "under blue sky in bright sunlight one need not search around"],
-        ],
-        columns=["docno", "text"],
-    )
-
-    print(docs_df)
-
-    indexer = pt.DFIndexer("./index_3docs", overwrite=True)
-    index_ref = indexer.index(docs_df["text"], docs_df["docno"])
-    index_ref.toString()
-    index = pt.IndexFactory.of(index_ref)
-
-
-if __name__ == "__main__":
-    run()

### 2023-11-26 crawler/index.py
feat: fastapi indexer
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@ -14,83 +14,118 @@ bm25 = pt.BatchRetrieve(index, wmodel="BM25")
 import pandas as pd
 import json
 import pyterrier as pt
+from fastapi import FastAPI
+from typing import Union
 
 
-def run():
-    if not pt.started():
-        pt.init()
+if not pt.started():
+    pt.init()
+app = FastAPI()
 
-    with open('saatchiart.json') as f:
+
+@app.get("/search")
+def search(query: str):
+    index = pt.IndexFactory.of('./index_saatchiart')
+    tf_idf = pt.BatchRetrieve(index, wmodel="TF_IDF")
+    output = tf_idf.search(query)
+    return output.to_dict()
+
+@app.post("/index/{index_name}")
+def index(index_name: str):
+    with open(index_name + '.json') as f:
         data = json.load(f)
         df = pd.DataFrame(data)
-        df['docno'] = [f'd{i + 1}' for i in range(len(df))]
+        df['docno'] = [f'd{i + 1}' for i in range(len(df))]     # add docno column to doc entries
         df.info()
         pd_indexer = pt.DFIndexer('./index_saatchiart', overwrite=True)
-        # index columns of dataframe
-        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno']) # add tags
+        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno'])     # TODO: add tags
         index = pt.IndexFactory.of(index_ref)
         print('Index stats: ', index.getCollectionStatistics().toString())
         print('lexicon: ')
         for kv in index.getLexicon():
             print(f'{kv.getKey()} -> {kv.getValue().toString()}')
 
-    return
+    return  {}
 
 
-    with open('artsyresult.json') as f:
-        data = json.load(f)
 
-        # Use pd.json_normalize to convert the JSON to a DataFrame
-        df = pd.json_normalize(data,
-                               meta=['image', 'author', 'title', 'price', 'url'])
 
-        # Add a 'docno' column to the DataFrame
-        df['docno'] = [str(i) for i in range(1, len(df) + 1)]
 
-        # Display the DataFrame
-        print(df)
+# if __name__ == '__main__':
+#     if not pt.started():
+#         pt.init()
+#     index = pt.IndexFactory.of('./index_saatchiart')
+#     tf_idf = pt.BatchRetrieve(index, wmodel="TF_IDF")
+#     output = tf_idf.search("nature")
+#     print(output)
 
[…]

### 2023-11-26 backend/ArtFinderSale/urls/__init__.py
feat: integration backend
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@ -1,5 +1,5 @@
 from django.urls import path, include
 
 urlpatters = [
-    path("documents/", include("ArtFinderSale.urls.search"))
+    path("documents/", include(".search"))
 ]

### 2023-11-26 backend/ArtFinderSale/urls/search.py

@@ -2,5 +2,5 @@ from django.urls import path
 from ..views.search import get_documents
 
 urlpatterns = [
-    path("get-documents/", get_documents, name="get-documents")
+    path("get-documents/<str:query>", get_documents, name="get-documents")
 ]

### 2023-11-26 backend/ArtFinderSale/views/search.py

@@ -6,10 +6,11 @@ from ..models import Document
 import requests
 
 
-def get_documents(request):
+def get_documents(request, query):
     IP = os.getenv("IP_INDEX")
-    query = request.GET.get('query', '')
-    url = f"{IP}/search/{query}"
+    # query = request.GET.get('query', '')
+    print(f"QUERY ----------------> {query}")
+    url = f"{IP}/search?query={query}"
 
     try:
         response = requests.get(url)

### 2023-11-26 backend/ArtForSale/urls.py

@@ -23,12 +23,12 @@ from django.views.generic import TemplateView
 
 urlpatterns = [
     path("admin/", admin.site.urls),
+    path("api/", include("ArtForSale.urls")),
 ]
 vue3_routes = []
 if settings.DEBUG:
     vue3_routes += [
-        ("vue3-root", ""),
-        ("vue3-searchEngine", "test/"),
+        ("vue3-root", "")
     ]
 
 

### 2023-11-26 backend/ArtFinderSale/urls/__init__.py
Sad

@@ -1,5 +1,5 @@
 from django.urls import path, include
 
-urlpatters = [
+urlpatterns = [
     path("documents/", include(".search"))
 ]

### 2023-11-26 backend/ArtFinderSale/urls/__init__.py
Continuied fix

@@ -1,5 +1,5 @@
 from django.urls import path, include
 
 urlpatterns = [
-    path("documents/", include(".search"))
+    path("documents/", include("ArtFinderSale.views.search"))
 ]

### 2023-11-26 backend/ArtFinderSale/urls/search.py

@@ -1,5 +1,5 @@
 from django.urls import path
-from ..views.search import get_documents
+from ..views.searchs import get_documents
 
 urlpatterns = [
     path("get-documents/<str:query>", get_documents, name="get-documents")

### 2023-11-27 backend/ArtFinderSale/urls/__init__.py
Sono un genio

@@ -1,5 +1,5 @@
 from django.urls import path, include
 
 urlpatterns = [
-    path("documents/", include("ArtFinderSale.views.search"))
+    path("documents/", include("ArtFinderSale.urls.search"), name="get-documents")
 ]

### 2023-11-27 backend/ArtFinderSale/urls/search.py

@@ -2,5 +2,5 @@ from django.urls import path
 from ..views.searchs import get_documents
 
 urlpatterns = [
-    path("get-documents/<str:query>", get_documents, name="get-documents")
+    path("get-documents/<str:query>/", get_documents, name="get-documents"),
 ]

### 2023-11-27 backend/ArtForSale/urls.py

@@ -23,7 +23,7 @@ from django.views.generic import TemplateView
 
 urlpatterns = [
     path("admin/", admin.site.urls),
-    path("api/", include("ArtForSale.urls")),
+    path("api/", include("ArtFinderSale.urls")),
 ]
 vue3_routes = []
 if settings.DEBUG:

### 2023-11-27 backend/ArtFinderSale/migrations/0002_remove_document_id_document_docno.py
Sono sempre piu sveglio

@@ -1,0 +1,23 @@
+# Generated by Django 4.2.7 on 2023-11-27 09:33
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('ArtFinderSale', '0001_initial'),
+    ]
+
+    operations = [
+        migrations.RemoveField(
+            model_name='document',
+            name='id',
+        ),
+        migrations.AddField(
+            model_name='document',
+            name='docno',
+            field=models.CharField(default=0, max_length=50, primary_key=True, serialize=False, unique=True),
+            preserve_default=False,
+        ),
+    ]

### 2023-11-27 backend/ArtFinderSale/models/document.py

@@ -1,7 +1,7 @@
 from django.db import models
 
 class Document(models.Model):
-    id = models.AutoField(primary_key=True)
+    docno = models.CharField(max_length=50, unique=True, primary_key=True)
     title = models.CharField(max_length=255)
     description = models.CharField(max_length=500)
     url = models.CharField(max_length=255)

### 2023-11-27 backend/ArtFinderSale/views/searchs.py

@@ -7,15 +7,18 @@ import requests
 
 
 def get_documents(request, query):
-    IP = os.getenv("IP_INDEX")
+    IP = "http://localhost:8001"
     # query = request.GET.get('query', '')
     print(f"QUERY ----------------> {query}")
-    url = f"{IP}/search?query={query}"
+    url = f"{IP}/search?query={query} art"
 
     try:
+        print(url)
         response = requests.get(url)
         response.raise_for_status()
+
         json_response = response.json()
+        print(json_response)
 
         documents = []
         for docno in json_response.get("docno", []):

### 2023-11-27 backend/ArtFinderSale/views/populate_database.py
Started database population

@@ -1,0 +1,29 @@
+import json
+from ..models import Document
+import pandas as pd
+
+
+def populate_database():
+    with open('../../crawler/saatchiart.json') as f:
+        data = json.load(f)
+        df = pd.DataFrame(data)
+        df['docno'] = [f'd{i + 1}' for i in range(len(df))]  # add docno column to doc entries
+        df.info()
+
+    # Loop through DataFrame rows and create Document objects
+    for index, row in df.iterrows():
+        new_doc = Document(
+            title=row['title'],
+            author=row['author'],
+            description=row['description'],
+            url=row['url'],
+            image=row['img'],
+            tags=row['tags'],
+            price=row['price'],
+            docno=row['docno'],
+        )
+        new_doc.save()
+
+
+if __name__ == "__main__":
+    populate_database()

### 2023-11-27 backend/ArtFinderSale/views/populate_database.py
Sono sad

@@ -4,7 +4,8 @@ import pandas as pd
 
 
 def populate_database():
-    with open('../../crawler/saatchiart.json') as f:
+    print("POPULATING DB")
+    with open('../../../crawler/saatchiart.json') as f:
         data = json.load(f)
         df = pd.DataFrame(data)
         df['docno'] = [f'd{i + 1}' for i in range(len(df))]  # add docno column to doc entries

### 2023-11-27 backend/ArtFinderSale/views/searchs.py
Added things

@@ -1,6 +1,6 @@
 import json
 import os
-
+import pandas as pd
 from django.http import JsonResponse
 from ..models import Document
 import requests
@@ -11,6 +11,29 @@ def get_documents(request, query):
     # query = request.GET.get('query', '')
     print(f"QUERY ----------------> {query}")
     url = f"{IP}/search?query={query} art"
+
+    print("POPULATING DB")
+    file_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), 'saatchiresult.json')
+    with open(file_path) as f:
+        print(f)
+        data = json.load(f)
+        df = pd.DataFrame(data)
+        df['docno'] = [f'd{i + 1}' for i in range(len(df))]  # add docno column to doc entries
+        df.info()
+
+    # Loop through DataFrame rows and create Document objects
+    for index, row in df.iterrows():
+        new_doc = Document(
+            title=row['title'],
+            author=row['author'],
+            description=row['description'],
+            url=row['url'],
+            image=row['img'],
+            tags=row['tags'],
+            price=row['price'],
+            docno=row['docno'],
+        )
+        new_doc.save()
 
     try:
         print(url)

### 2023-11-27 backend/ArtFinderSale/views/searchs.py
Added things

@@ -12,28 +12,6 @@ def get_documents(request, query):
     print(f"QUERY ----------------> {query}")
     url = f"{IP}/search?query={query} art"
 
-    print("POPULATING DB")
-    file_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), 'saatchiresult.json')
-    with open(file_path) as f:
-        print(f)
-        data = json.load(f)
-        df = pd.DataFrame(data)
-        df['docno'] = [f'd{i + 1}' for i in range(len(df))]  # add docno column to doc entries
-        df.info()
-
-    # Loop through DataFrame rows and create Document objects
-    for index, row in df.iterrows():
-        new_doc = Document(
-            title=row['title'],
-            author=row['author'],
-            description=row['description'],
-            url=row['url'],
-            image=row['img'],
-            tags=row['tags'],
-            price=row['price'],
-            docno=row['docno'],
-        )
-        new_doc.save()
 
     try:
         print(url)

### 2023-11-28 backend/ArtFinderSale/views/searchs.py
Aiuto

@@ -16,6 +16,7 @@ def get_documents(request, query):
     try:
         print(url)
         response = requests.get(url)
+        new_response = requests.post("http://localhost:8001/index/results")
         response.raise_for_status()
 
         json_response = response.json()

### 2023-11-28 crawler/index.py

@@ -15,6 +15,7 @@ import pandas as pd
 import json
 import pyterrier as pt
 from fastapi import FastAPI
+import os
 from typing import Union
 
 
@@ -25,7 +26,7 @@ app = FastAPI()
 
 @app.get("/search")
 def search(query: str):
-    index = pt.IndexFactory.of('./index_saatchiart')
+    index = pt.IndexFactory.of('./index_total')
     tf_idf = pt.BatchRetrieve(index, wmodel="TF_IDF")
     output = tf_idf.search(query)
     return output.to_dict()
@@ -33,12 +34,18 @@ def search(query: str):
 @app.post("/index/{index_name}")
 def index(index_name: str):
     with open(index_name + '.json') as f:
+        print(index_name + ".json")
         data = json.load(f)
         df = pd.DataFrame(data)
         df['docno'] = [f'd{i + 1}' for i in range(len(df))]     # add docno column to doc entries
+        result_json = df.to_json(orient = 'records')
+        print(result_json)
+        output_file_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), f'final_result.json')
+        with open(output_file_path, 'w') as output_file:
+            output_file.write(result_json)
         df.info()
-        pd_indexer = pt.DFIndexer('./index_saatchiart', overwrite=True)
-        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno'])     # TODO: add tags
+        pd_indexer = pt.DFIndexer('./index_total', overwrite=True)
+        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno'], df['tags'])     # TODO: add tags
         index = pt.IndexFactory.of(index_ref)
         print('Index stats: ', index.getCollectionStatistics().toString())
         print('lexicon: ')

### 2023-11-29 backend/ArtFinderSale/migrations/0003_document_author.py
Almost done

@@ -1,0 +1,19 @@
+# Generated by Django 4.2.7 on 2023-11-29 10:58
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('ArtFinderSale', '0002_remove_document_id_document_docno'),
+    ]
+
+    operations = [
+        migrations.AddField(
+            model_name='document',
+            name='author',
+            field=models.CharField(default=1, max_length=250),
+            preserve_default=False,
+        ),
+    ]

### 2023-11-29 backend/ArtFinderSale/migrations/0004_alter_document_price.py

@@ -1,0 +1,18 @@
+# Generated by Django 4.2.7 on 2023-11-29 10:59
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('ArtFinderSale', '0003_document_author'),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name='document',
+            name='price',
+            field=models.CharField(max_length=20, null=True),
+        ),
+    ]

### 2023-11-29 backend/ArtFinderSale/migrations/0005_alter_document_author_alter_document_tags_and_more.py

@@ -1,0 +1,28 @@
+# Generated by Django 4.2.7 on 2023-11-29 11:00
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('ArtFinderSale', '0004_alter_document_price'),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name='document',
+            name='author',
+            field=models.CharField(max_length=250, null=True),
+        ),
+        migrations.AlterField(
+            model_name='document',
+            name='tags',
+            field=models.JSONField(default=list, null=True),
+        ),
+        migrations.AlterField(
+            model_name='document',
+            name='title',
+            field=models.CharField(max_length=255, null=True),
+        ),
+    ]

### 2023-11-29 backend/ArtFinderSale/models/document.py

@@ -1,13 +1,15 @@
 from django.db import models
 
+
 class Document(models.Model):
     docno = models.CharField(max_length=50, unique=True, primary_key=True)
-    title = models.CharField(max_length=255)
+    title = models.CharField(max_length=255, null=True)
     description = models.CharField(max_length=500)
+    author = models.CharField(max_length=250, null=True)
     url = models.CharField(max_length=255)
     image = models.CharField(max_length=255)
-    tags = models.JSONField(default=list)
-    price = models.CharField(max_length=20)
+    tags = models.JSONField(default=list, null=True)
+    price = models.CharField(max_length=20, null=True)
 
     def __str__(self):
         return self.title

### 2023-11-29 backend/ArtFinderSale/views/searchs.py

@@ -12,32 +12,44 @@ def get_documents(request, query):
     print(f"QUERY ----------------> {query}")
     url = f"{IP}/search?query={query} art"
 
-
     try:
         print(url)
         response = requests.get(url)
-        new_response = requests.post("http://localhost:8001/index/results")
         response.raise_for_status()
+        # with open('ArtFinderSale/views/final_result.json', 'r') as json_file:
+        #     data = json.load(json_file)
+        #
+        # # Assuming the JSON structure is a list of dictionaries
+        # for row in data:
+        #
+        #     new_document = Document(
+        #         image=row['img'],
+        #         author=row['author'],
+        #         title=row['title'],
+        #         description=row['description'],
+        #         price=row['price'],
+        #         tags=row['tags'],
+        #         url=row['url'],
+        #         docno = row['docno']
+        #     )
+        #     new_document.save()
 
         json_response = response.json()
-        print(json_response)
+
 
         documents = []
-        for docno in json_response.get("docno", []):
-            try:
-                current_doc = Document.objects.get(docno=docno)
-                documents.append({
-                    'docno': current_doc.docno,
-                    'title': current_doc.title,
-                    'description': current_doc.description,
-                    'url': current_doc.url,
-                    'image': current_doc.image,
-                    'tags': current_doc.tags,
-                    'price': current_doc.price,
-                })
-            except Document.DoesNotExist:
-                pass
-
+        for docno in json_response["docno"].values():
+            current_doc = Document.objects.get(docno=docno)
+            documents.append({
+                'docno': current_doc.docno,
+                'title': current_doc.title,
+                'description': current_doc.description,
+                'url': current_doc.url,
+                'image': current_doc.image,
+                'tags': current_doc.tags,
+                'price': current_doc.price,
+            })
+        print(documents)
         return JsonResponse({"documents": documents})
     except requests.exceptions.RequestException as e:
         return JsonResponse({'error': str(e)}, status=500)

### 2023-11-29 crawler/crawler/spiders/artsy_spyder.py
Other modifications

@@ -70,7 +70,8 @@ class ArtsySpider(scrapy.Spider):
                'title': title, 
                'price': price ,
                'url' : response.url,
-               'tag': tag}
+               'description' : "",
+               'tag': [tag]}
 
     @staticmethod
     def get_description():

### 2023-11-29 crawler/index.py

@@ -16,13 +16,25 @@ import json
 import pyterrier as pt
 from fastapi import FastAPI
 import os
+from fastapi.middleware.cors import CORSMiddleware
 from typing import Union
 
 
 if not pt.started():
     pt.init()
 app = FastAPI()
+origins = [
+    "http://localhost:5173",
+    "http://localhost:8000",
+]
 
+app.add_middleware(
+    CORSMiddleware,
+    allow_origins=origins,
+    allow_credentials=True,
+    allow_methods=["*"],
+    allow_headers=["*"],
+)
 
 @app.get("/search")
 def search(query: str):
@@ -39,13 +51,12 @@ def index(index_name: str):
         df = pd.DataFrame(data)
         df['docno'] = [f'd{i + 1}' for i in range(len(df))]     # add docno column to doc entries
         result_json = df.to_json(orient = 'records')
-        print(result_json)
         output_file_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), f'final_result.json')
         with open(output_file_path, 'w') as output_file:
             output_file.write(result_json)
         df.info()
         pd_indexer = pt.DFIndexer('./index_total', overwrite=True)
-        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno'], df['tags'])     # TODO: add tags
+        index_ref = pd_indexer.index(df['author'], df['title'], df['description'], df['docno'])     # TODO: add tags
         index = pt.IndexFactory.of(index_ref)
         print('Index stats: ', index.getCollectionStatistics().toString())
         print('lexicon: ')

### 2023-11-29 frontend/src/main.ts

@@ -11,8 +11,8 @@ import App from './App.vue'
 import router from './router'
 
 const app = createApp(App)
-
-app.use(createPinia())
+const pinia = createPinia()
+app.use(pinia)
 app.use(router)
 app.use(PrimeVue)
 app.mount('#app')

### 2023-11-29 frontend/src/stores/document.ts

@@ -13,6 +13,7 @@ export const useDocumentStore = defineStore({
         async getDocuments(query: string) {
             try {
                 const response = await axios.get(`http://localhost:8000/api/documents/get-documents/${query}/`);
+                console.log(response)
                 this.documents = response.data.documents;
             } catch (error) {
                 console.error("Error fetching fields:", error);

### 2023-11-29 backend/ArtFinderSale/urls/__init__.py
Added things

@@ -1,5 +1,6 @@
 from django.urls import path, include
 
 urlpatterns = [
-    path("documents/", include("ArtFinderSale.urls.search"), name="get-documents")
+    path("documents/", include("ArtFinderSale.urls.search"), name="get-documents"),
+    # path("recomandation/", include("ArtFinderSale.urls.search"), name="get-recommended")
 ]

### 2023-11-29 backend/ArtFinderSale/urls/search.py

@@ -1,6 +1,7 @@
 from django.urls import path
-from ..views.searchs import get_documents
+from ..views.searchs import get_documents, get_recommended
 
 urlpatterns = [
     path("get-documents/<str:query>/", get_documents, name="get-documents"),
+    # path("get-recomended/<str_list:query>/", get_recommended, name="get-recommended"),
 ]

### 2023-11-29 backend/ArtFinderSale/views/searchs.py

@@ -44,6 +44,7 @@ def get_documents(request, query):
                 'docno': current_doc.docno,
                 'title': current_doc.title,
                 'description': current_doc.description,
+                'author': current_doc.author,
                 'url': current_doc.url,
                 'image': current_doc.image,
                 'tags': current_doc.tags,
@@ -53,3 +54,20 @@ def get_documents(request, query):
         return JsonResponse({"documents": documents})
     except requests.exceptions.RequestException as e:
         return JsonResponse({'error': str(e)}, status=500)
+
+
+def get_recommended(request, query):
+    answers = []
+    for tag in query:
+        IP = "http://localhost:8001"
+        # query = request.GET.get('query', '')
+        url = f"{IP}/search?query={tag} art"
+        response = requests.get(url)
+        response.raise_for_status()
+        answers.append(response.json())
+
+    results = []
+    for i in range(1, 10):
+        results.append(answers[i])
+
+    print(results)

### 2023-11-29 backend/ArtForSale/settings.py

@@ -37,6 +37,7 @@ INSTALLED_APPS = [
     "django.contrib.sessions",
     "django.contrib.messages",
     "django.contrib.staticfiles",
+    "corsheaders",
     "ArtFinderSale"]
 
 MIDDLEWARE = [
@@ -47,7 +48,23 @@ MIDDLEWARE = [
     "django.contrib.auth.middleware.AuthenticationMiddleware",
     "django.contrib.messages.middleware.MessageMiddleware",
     "django.middleware.clickjacking.XFrameOptionsMiddleware",
+    "corsheaders.middleware.CorsMiddleware",
+    "django.middleware.common.CommonMiddleware",
 ]
+
+CORS_ALLOWED_ORIGINS = [
+    "http://localhost:5173",
+    "http://localhost:8001",
+]
+
+CORS_ALLOW_METHODS = (
+    "DELETE",
+    "GET",
+    "OPTIONS",
+    "PATCH",
+    "POST",
+    "PUT",
+)
 
 ROOT_URLCONF = "ArtForSale.urls"
 

### 2023-11-29 frontend/src/stores/document.ts

@@ -5,6 +5,7 @@ export const useDocumentStore = defineStore({
     id: "documents",
     state: () => ({
         documents: [],
+        recomandations: [],
     }),
     getters: {
         hasFields: (state) => state.documents.length > 0,
@@ -15,6 +16,15 @@ export const useDocumentStore = defineStore({
                 const response = await axios.get(`http://localhost:8000/api/documents/get-documents/${query}/`);
                 console.log(response)
                 this.documents = response.data.documents;
+            } catch (error) {
+                console.error("Error fetching fields:", error);
+                throw error;
+            }
+        },
+        async getRecomended(query: array) {
+            try {
+                const response = await axios.get(`http://localhost:8000/api/recomandation/get-recomended/${query}/`);
+                console.log(response)
             } catch (error) {
                 console.error("Error fetching fields:", error);
                 throw error;

### 2023-11-29 backend/ArtFinderSale/views/searchs.py
Added things

@@ -10,7 +10,7 @@ def get_documents(request, query):
     IP = "http://localhost:8001"
     # query = request.GET.get('query', '')
     print(f"QUERY ----------------> {query}")
-    url = f"{IP}/search?query={query} art"
+    url = f"{IP}/search?query={query}"
 
     try:
         print(url)

### 2023-11-29 crawler/index.py

@@ -39,7 +39,7 @@ app.add_middleware(
 @app.get("/search")
 def search(query: str):
     index = pt.IndexFactory.of('./index_total')
-    tf_idf = pt.BatchRetrieve(index, wmodel="TF_IDF")
+    tf_idf = pt.BatchRetrieve(index, wmodel="BM25")
     output = tf_idf.search(query)
     return output.to_dict()
 

### 2023-12-08 docs/report/progress.tex
refactor: latex reports
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

--- 2023-11-26 docs/report/progress/article.tex
@@
 \documentclass[12pt]{spieman}  % 12pt font required by SPIE;
-%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
+%\documentclass[a4paper,12pt]{spieman}  % use this instead forA4 paper
 \usepackage{amsmath,amsfonts,amssymb}
@@
 \cftpagenumbersoff{table} 
+\thispagestyle{empty}
+
 \begin{document}
@@
 \end{document}
-
-\subsection{Use of This Document}
-
-This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.
-The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it.
-Authors may use it as a template to create their own manuscript.
-While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.
-
-\subsection{English}
-
-Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-In addition, good English usage is essential.
-Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced.
-Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}.
-SPIE authors will receive a 15\% discount off their services.
-A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission.
-Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.
-
-\subsection{Page Setup and Fonts}
-
-All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm).
-Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.
-
-The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}.
-If this font is not available, use a similar serif font.
-The manuscript should not contain headers or footers.
-Pages should be numbered.
-
-\begin{table}[ht]
-\caption{Fonts sizes and styles.} 
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
-\hline\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Parts of Manuscript}
-
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
-
-\subsection{Title and Author Information}
-\label{sect:title}
-The article title appears left justified at the top of the first page.
-The title font is 16 pt., bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.).
-The word ``novel'' should not appear in the title, as publication will imply novelty.
-Avoid the use of acronyms in the title, unless they are widely understood.
-
-The list of authors immediately follows the title, 18 points below.
-The font is 12 pt., bold and the author names are left justified.
-The author affiliations and addresses follow the names, in 10-pt., normal font and left justified.
-For multiple affiliations, each affiliation should appear on a separate line.
-Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations.
-The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.
-
-\subsection{Abstract}
-The abstract should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting journals, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-Please note that the following journals require the use of structured abstracts in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Medical Imaging}.
-Structured abstracts are encouraged for the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}.
-Helpful guidelines for structured abstracts are available on the website of the journal.
-
-\subsection{Subject terms/Keywords}
-Keywords are required. Please provide 3-6 keywords related to your paper.
-
-\subsection{Body of Paper}
-The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.
-
-To provide transition elements in your paper, it is important to refer back (or forward) to specific sections.
-Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out.
-When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.
-
-At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).
-
-\subsection{Footnotes}
-Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided.
-If absolutely necessary, the footnote mark must come at the end of a sentence.
-To insert a footnote, use the {\verb|\footnote{}|} command.
-
-\subsection{Appendices}
-Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms.
-Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.
-
-\subsection{Disclosures}
-Conflicts of interest should be declared under a separate header.
-If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest.
-For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}
-
-\subsection{Code, Data, and Materials Availability}
-In support of open scientific exchange, SPIE journals require Data and Code Availability Statements in all accepted papers.
-This requirement went into effect on 1 May 2023.
-These statements should describe how to access any data that would be required to replicate or interpret the findings reported in the paper.
-
-\subsection{Acknowledgments}
-Acknowledgments and funding information should be added after the conclusion, and before references.
-Include grant numbers and the full name of the funding body.
-The acknowledgments section does not have a section number.
-
-\subsection{References}
-The References section lists books, articles, and reports that are cited in the paper.
-This section does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
-
-The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-The references are numbered in the order of their first citation.
-Citations to the references are made using superscripts, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them.
-Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.
-
-\subsubsection{Reference linking and DOIs}
-A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet.
-The use of DOIs allows readers to easily access cited articles.
-Authors should include the DOI at the end of each reference in brackets if a DOI is available.
-See examples at the end of this manuscript.
-A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}.
-The inclusion of DOIs will facilitate reference linking and is highly recommended.
-
-In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}.
-The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.
-
-\subsection{Biographies}
-A brief professional biography of approximately 75 words may be provided for each author, if available.
-Biographies should be placed at the end of the paper, after the references.
-Personal information such as hobbies or birthplace/birthdate should not be included.
-Author photographs are not published.
-
-\section{Section Formatting}
-\label{sect:sections}
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references.
-(Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.
-
-Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation.
-There is no additional space between paragraphs.
-In LaTeX, paragraphs are separated by blank lines in the source file.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
-
-\subsection{Subsection Headings}
-All important words in a subsection (level 1) header are capitalized.
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end.
-The heading is left justified and its font is 12 pt.
-italic.
-
-\subsubsection{Sub-subsection headings}
-The first word of a sub-subsection is capitalized.
-The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known).
-The heading is left justified and its font is 11 pt.
-italic.
-
-\section{Figures and Tables}
-
-\subsection{Figures}
-
-Figures are numbered in the order in which they are called out in the text.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It may be necessary to move figures or tables around to enhance readability.
-LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.
-
-Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered.
-Figure captions are centered below the figure or graph.
-Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt.
-font.
-See Fig.~\ref{fig:example} for an example.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[height=5.5cm]{mcr3b.eps}
-\end{tabular}
-\end{center}
-\caption 
-{ \label{fig:example}
-Example of a figure caption. } 
-\end{figure}
-
-Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.
-In no case, should the article's text be wrapped around a figure.
-Figure~\ref{fig:example2} shows two side-by-side images.
-When a figure contains more than one image, the author must submit them as a single image file.
-Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
-\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-\\
-(a) \hspace{5.1cm} (b)
-\end{tabular}
-\end{center}
-\caption 
-{ \label{fig:example2}
-Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
-\end{figure}
-
-\subsection{Tables}
-Tables are numbered in the order in which they are referenced.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It is preferable to have tables appear at the top or bottom of the page, if possible.
-Table captions are handled identically to those for figures, except that they appear above the table.
-See Table~\ref{tab:fonts} for an example.
-
-\subsection{Video}
-Acceptable file formats, including MOV (.mov), MPEG (.mpg), and MP4 (.mp4), are playable using standard media players, such as VLC or Windows Media Player.
-The recommended maximum size for each video file is 10-12 MB.
-Authors may insert a representative still image from the video file in the manuscript as a figure.
-The caption label will be linked by the publisher to the actual video file.
-The video may also be mentioned in an existing figure caption.
-Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.
-The video number, file type, and file size should be included in parentheses at the end of the figure caption.
-See Figure \ref{vid:satellite} for an example.
-
-\begin{video}
-\begin{center}
-{\includegraphics[height=5cm]{satellite.eps}}
-\\
-\end{center}
-\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
-\end{video}
-
-\appendix    % this command starts appendixes
-
-\section{Miscellaneous Formatting Details}
-\label{sect:misc}
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.
-
-\subsection{Formatting Equations}
-Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the field of view is
-\begin{equation}
-\label{eq:fov}
-2 a = \frac{(b + 1)}{3c} \, ,
-\end{equation}
-where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.
-
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma appears after the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
-
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise.
-Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..
-
-\subsection{Formatting Theorems}
-
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.
-The text of the theorem continues on the same line in normal, 10-pt.
-font, achieved in LaTeX using \verb|\footnotesize|.
-For example,
-
-\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}
-
-% \disclosures 
-\subsection*{Disclosures}
-Conflicts of interest should be declared under a "Disclosures" header.
-If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.
-
-\subsection* {Code, Data, and Materials Availability} 
-In support of open scientific exchange, SPIE journals require Code, Data, and Materials Availability Statements in all accepted papers.
-This requirement went into effect on 1 May 2023.
-These statements should describe how to access any data that would be required to replicate or interpret the findings reported in the paper.
-Authors are encouraged to make the data and code related to the manuscript publicly available whenever possible, and utilize repositories that are well-known to the field (FigShare, Github, CodeOcean, etc.).
-If the data or code cannot be made publicly available, the authors should state the reason and explain how it can be obtained.
-Likewise, if data sharing is not applicable, the statement must say so.
-Example statements may be found in the Author Guidelines for the journal.
-
-\subsection* {Acknowledgments}
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
-
-%%%%% References %%%%%
-
-\bibliography{report}   % bibliography data in report.bib
-\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst
-
-%%%%% Biographies of authors %%%%%
-
-\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering.
-He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.
-He is the author of more than 50 journal papers and has written three book chapters.
-His current research interests include optical interconnects, holography, and optoelectronic systems.
-He is a member of SPIE.
-
-\vspace{1ex}
-\noindent Biographies and photographs of the other authors are not available.
-
-\listoffigures
-\listoftables
-
-\end{spacing}
-\end{document}

### 2023-12-08 docs/report/submission.tex
refactor: latex reports
Co-authored-by: Filippo Piloni <filippo.piloni@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\title{Information Retrieval - Submission Report \\Project N.14: Art For Sale}

\author{Jeferson Morales Mariciano}
\author{Filippo Piloni}
\affil{Università della Svizzera italiana, Faculty of Informatics, Lugano, Switzerland}

\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document}
\maketitle
\tableofcontents

\begin{spacing}{1}   % use double spacing for rest of manuscript

    \section{Introduction}
    ArtForSale aims to be a search engines aimed to display artworks from across various sites, offering to the user a friendly and intuitive interface.\newline
    For this project, the following features has been implemented:
    \begin{itemize}
        \item Result presentation
        \item Filtering
        \item Automatic recommendation
    \end{itemize}

    \section{Technologies Used}
    \subsection{Scrapy}
    Scrapy, a Python framework for web crawling and scraping, is utilized in to initiate the crawling/scraping process for a specified set of artworks. The extracted data is subsequently channeled into a .json file.
    \subsection{PyTerrier}
    PyTerrier is a Python library that provides a high-level interface for the Terrier information retrieval system. In the provided code snippet, PyTerrier is used for building an information retrieval system to search and index documents.\newline
    Our index.py file uses PyTerrier to create the index starting from the .json file

    \subsection{Django \& SQLite}
    The main part of the project has been carried using a Django based backend. The backend handles the main fetches from the frontend.
    The backend is also the joint between the frontend and the index, making calls to a FASTApi that returns relevant documents given a query.\newline
    To return to the frontend the main information about the documents, the backend iterates through a database in SQLite that contains the main information for each artwork

    \subsection{Vue.js \& PrimeVue}
    Finally, to develop the frontend, it has been used Vue.js, using the PrimeVue as UI library. Vue.js allows us to create a reactive and dynamic user interface, while PrimeVue provides us with a set of pre-built components and styles.

    \section{Crawling and Indexing}

    \section{Backend}
    The backend relies on a SQLite database to store the main information about the documents, making possible to retrieve the relevant ones following a call to the index.\newline
    Django serves as the foundational framework for constructing the primary structure, bringing with it a multitude of advantages such as rapid development, a robust and secure architecture, built-in administrative features, and a thriving community support ecosystem.\newline
    The backend handles the two main fetches of the application:
    \begin{itemize}
        \item /api/documents/get-documents/"query"/: This endpoint facilitates the retrieval of relevant documents based on a provided query string.
        \item /api/recommendation/get-recommended/: This endpoint is tasked with retrieving recommended artworks. By inputting a set of tags, it conducts a search within the index, returning all pertinent documents associated with the specified criteria.
    \end{itemize}
    \section{Frontend}
    The frontend is the main part of the application, where all the features are implemented.\newline
    For the interface, it has been chosen a simple layout, consisting of only a search-bar and a search button. Once the user performs the search, the aspect of the page changes, adding new components. We will examine each of them:
    \begin{itemize}
        \item First, under the search-bar will appear a new set of control to filter the obtained results according to four main characteristics: site of origin, minimum price, maximum price and tag.
        \item Second, there will be shown some carousels for the recommended results based on the most frequents tags of the resulted artworks. Essentially, once all the artworks related to the query have been retrieved, the frontend extracts from all these artworks the related tags, it chooses the ones with the higher frequency and, using the /api/recommendation/get-recommended/ fetch, it shows a maximum of 5 results related to each tag in a moving carousel
        \item Finally, the artworks retrieved from the query are displayed in a card-like style, showing an insight of the artwork, the author, the title, the price, a short description and the main tags, with a Visit button that will bring the user to the page of that artwork in the original site
    \end{itemize}
    \section{User Evaluation}

    \section{Running information}

    \section{Conclusions}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{spacing}
\end{document}

### 2023-12-09 docs/report/submission.tex
feat: report submission start
Co-authored-by: Filippo Piloni <pilonf@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
 \usepackage{tocloft}
+\usepackage{hyperref}
 \title{Information Retrieval - Submission Report \\Project N.14: Art For Sale}
@@
 \begin{document}
+
 \maketitle
 \tableofcontents
+\newpage
 
@@
     \section{Introduction}
-    ArtForSale aims to be a search engines aimed to display artworks from across various sites, offering to the user a friendly and intuitive interface.\newline
+    The Information Retrieval course project \textit{"ArtForSale"} aims to be a working prototype of an information
+    retrieval system for a specific task: to display for-sale artworks from art selling related websites
+    listed in Section \ref{sec:websites}.
+    The system has around $\approx 8,500$ indexed documents served through a
+    user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.
+
+    \subsection{Websites}\label{sec:websites}
+    The following websites were chosen for the project based on availability of data, ease of scraping and
+    low restrictions regarding policies and terms of use to scrape documents i.e. \textit{robots.txt} rules:
+
+    \begin{itemize}
+        \item \url{www.artsy.net}
+        \item \url{www.artfinder.com}
+        \item \url{www.saatchiart.com}
+    \end{itemize}
+
+    The total cumulative number of documents gathered from the above websites is $\approx 8,500$ stored in
+    \textit{results.json} file containing the list of documents in JSON format.
+    Further information concerning the scraping process and implementation is discussed
+    in Crawler Section \ref{sec:crawling}.
+
+    \subsection{Features}
     For this project, the following features has been implemented:
@@
 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Technologies Used}
+
     \subsection{Scrapy}
@@
 The extracted data is subsequently channeled into a .json file.
+
     \subsection{PyTerrier}
@@
 
-    \section{Crawling and Indexing}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \section{Crawling}\label{sec:crawling}
+    \section{Indexing}\label{sec:indexing}
 
@@
     \end{itemize}
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Frontend}
@@
     \end{itemize}
+
+    \subsection{User Interface}\label{sec:ui}
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{User Evaluation}
 
+    \subsection{User Experience}\label{sec:ux}
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Running information}
 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Conclusions}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{spacing}

### 2023-12-09 docs/report/submission.tex
feat: report USI logo for cover
Co-authored-by: Filippo Piloni <pilonf@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
 \usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage{wrapfig}
 \title{Information Retrieval - Submission Report \\Project N.14: Art For Sale}
@@
 
+\begin{wrapfigure}{l}{0.25\textwidth}
+    \includegraphics[width=0.25\textwidth, trim={0cm 0cm 0cm 7cm}]{USI_logo.png}
+\end{wrapfigure}
+
 \maketitle
@@
     listed in Section \ref{sec:websites}.
-    The system has around $\approx 8,500$ indexed documents served through a
+    The system has around $\approx 8,500$ indexed documents for searching, browsing and presented through a
     user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.
@@
     \subsection{Features}
-    For this project, the following features has been implemented:
+    For this project, the following features have been implemented:
     \begin{itemize}
@@
     \section{User Evaluation}
+    System evaluation: Recall and precision paragraph
 

### 2023-12-09 docs/report/submission.tex
feat: report added features description
Co-authored-by: Filippo Piloni <pilonf@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     \subsection{Features}
-    For this project, the following features have been implemented:
+    The course project requires 2 additional categorized features to be implemented besides the retrieval system:
+    1 each from simple and complex group features.
+
+    The following features have been implemented:
     \begin{itemize}
-        \item Result presentation
-        \item Filtering
-        \item Automatic recommendation
+        \item Simple
+              \begin{itemize}
+                  \item \textbf{Result presentation}:
+                        results should be presented in a tabular format so that many results could be seen at the same time.
+                        Each table cell should contain appropriate information for your project.
+                  \item \textbf{Filtering}:
+                        in addition to being able to search by title, an user should be able to filter the
+                        results based on at least 3 relevant attributes for your project.
+              \end{itemize}
+
+        \item Complex
+              \begin{itemize}
+                  \item \textbf{Automatic recommendation}:
+                        In addition to the relevant search results pertaining to the user query,
+                        the user should also be suggested "similar" products based on, say, category, description,
+                        price etc. The ordering among the recommended items is not important.
+                        However, you should mention how did you arrive at the recommendations.
+                        For this purpose, you can use any open-source recommenders available.
+              \end{itemize}
     \end{itemize}

### 2023-12-10 docs/report/submission.tex
feat: submssion report architecture image
Starting its sections

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
 
-    The total cumulative number of documents gathered from the above websites is $\approx 8,500$ stored in
-    \textit{results.json} file containing the list of documents in JSON format.
+    The cumulative number of documents gathered from the above websites is around $\approx 8,500$ stored in
+    \textit{results.json} file containing the list of samples in JSON format.
     Further information concerning the scraping process and implementation is discussed
@@
     The course project requires 2 additional categorized features to be implemented besides the retrieval system:
-    1 each from simple and complex group features.
+    1 each from simple and complex group features.\\
+    The \textit{Art For Sale} project implements 2 + 1 bonus additional simple features:
 
-    The following features have been implemented:
     \begin{itemize}
@@
 
+    Shown results are sorted in descending order of relevance from left to right in the tabular view.\\
+    Implementation details of features are on Architecture Section \ref{sec:architecture}.\\
+    Moreover, by exploiting the automatic recommandation feature implemented using category tags
+    and the filtering feature to filter them,
+    the \textbf{Results clustering} complex feature was tackled by allowing to
+    group the results into topics based on category tags.
+    Though, a negative filter to exclude documents based on categories was not added,
+    thus partially implementing the feature.\\
+
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{Technologies Used}
+    \section{Architecture}\label{sec:architecture}
 
-    \subsection{Scrapy}
+    \begin{figure}[H]
+        \centering
+        \caption{Search Engine Architecture of \textit{ArtForSale} project}
+        \label{fig:architecture}
+        \includegraphics[width=\textwidth, trim={0cm 16cm 0cm  3cm}]{figures/architecture.pdf}
+    \end{figure}
+
+    The project Information Retrieval system has the capabilities limited to a Text retrieval.
+
+    Text Access, access mode: pull and push, query and browsing
+    INFORMATION SHORT TERM NEEDS
+
+    Filtering and RECOMMENDATION SYSTEM: information needs: LONG TERM NEEDS
+
+    browser traces collected in cookies for every search query user issues, part of recommender system.
+
+    \subsection{Tech Stack}
+
+    \subsubsection{Scrapy}
     Scrapy, a Python framework for web crawling and scraping, is utilized in to initiate the crawling/scraping process for a specified set of artworks.
@@
 
-    \subsection{PyTerrier}
+    \subsubsection{PyTerrier}
     PyTerrier is a Python library that provides a high-level interface for the Terrier information retrieval system.
@@
 
-    \subsection{Django \& SQLite}
+    \subsubsection{Django \& SQLite}
     The main part of the project has been carried using a Django based backend. The backend handles the main fetches from the frontend.
@@
 
-    \subsection{Vue.js \& PrimeVue}
+    \subsubsection{Vue.js \& PrimeVue}
     Finally, to develop the frontend, it has been used Vue.js, using the PrimeVue as UI library.
@@
     \section{Crawling}\label{sec:crawling}
+
     \section{Indexing}\label{sec:indexing}
+    The Pyterrier platform supports indexing and retrieval operations by employing NLP techniques
+    to enable computers to understand the meaning of natural language text.
 
@@
 
+    Emotional design: key in Apple, Google alike
+
+    Jacobs heuristics respected
+
+    standard filtering system
+
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{Running information}
+    %\section{Running information}
+    \section{Limitations and Future Improvements}
+
+    The project is a \textit{Text Retrieval} system at its current state.
+    Since the type of data provided by artworks is not descriptive nor verbose,
+    implementing \textit{Text Analysis} features becomes troublesome because lacking the large amounts of
+    text data in order to discover interesting patterns buried in text.
+    Nevertheless, \textit{Text Organization} implementation feasibility is high due to
+    short well-structured categorized-based descriptions usually artwork documents have,
+    allowing to connect and navite scattered information.
 

### 2023-12-10 docs/report/submission.tex
feat: submission report TIS part
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     Though, a negative filter to exclude documents based on categories was not added,
-    thus partially implementing the feature.\\
+    thus partially implementing another extra feature.\\
 
@@
     \section{Architecture}\label{sec:architecture}
+
+    The \textbf{Information Retrieval System} has capabilities limited to a
+    \textbf{TIS} \footnote{Text Information System}
+    with \textbf{Text retrieval}.\\
+    The \textbf{Text Access} part helping users to retrieve the right information at the right time,
+    is structured by connecting the system with users in both modes:
+    \begin{itemize}
+        \item \textbf{Pull}: user takes initiative to fetch ad-hoc relevant information from the system,
+              which offers \textbf{querying} and \textbf{browsing} capabilities.
+              Satisfies \textbf{short-term needs}.
+        \item \textbf{Push}: system takes initiative and has good knowledge of what are the user's
+              \textbf{long-term needs} of information throughout the filtering and recommendation system
+              using \textbf{browsing traces} to model the behavior of the user.
+    \end{itemize}
 
@@
 
-    The project Information Retrieval system has the capabilities limited to a Text retrieval.
+    \newpage
+    \textbf{browser traces} collected in cookies for every search query user issues, part of recommender system.
 
-    Text Access, access mode: pull and push, query and browsing
-    INFORMATION SHORT TERM NEEDS
-
-    Filtering and RECOMMENDATION SYSTEM: information needs: LONG TERM NEEDS
-
-    browser traces collected in cookies for every search query user issues, part of recommender system.
-
-    \subsection{Tech Stack}
+    \subsection{Technology Stack}
 
@@
     \section{Crawling}\label{sec:crawling}
+    Harnesing (relatively) Bit Text Data characterized with the 5
+    Vs \footnote{Volume, Variety, Velocity, Value, Veracity},
+    we lack automating the Velocity attribute since we need to rerun the spiders manually to update its
+    status on the inverted index.
+    Crawling parses text that is unstructed to group them in well-structured documents, allowing them to be
+    easily indexed.
 
     \section{Indexing}\label{sec:indexing}
-    The Pyterrier platform supports indexing and retrieval operations by employing NLP techniques
-    to enable computers to understand the meaning of natural language text.
+    The Pyterrier platform supports indexing and retrieval operations by employing shallow
+    NLP \footnote{Natural Language Processing}
+    techniques to enable computers to understand the meaning of natural language text.
 
-    \section{Backend}
+    \section{Retrieval}
+    \subsection{Backend}
     The backend relies on a SQLite database to store the main information about the documents, making possible to retrieve the relevant ones following a call to the index.\newline
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{Frontend}
+    \subsection{Frontend}
     The frontend is the main part of the application, where all the features are implemented.\newline
@@
 
-    \subsection{User Interface}\label{sec:ui}
+    \subsubsection{User Interface}\label{sec:ui}
 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{User Evaluation}
+    \section{Evaluation}
     System evaluation: Recall and precision paragraph
 
-    \subsection{User Experience}\label{sec:ux}
+    \subsection{User Evaluation}
+
+    SUS includes pia, quote are designers users too?
+
+    \subsubsection{User Experience}\label{sec:ux}
+    Sentiment analysis
 
@@
     short well-structured categorized-based descriptions usually artwork documents have,
-    allowing to connect and navite scattered information.
+    allowing to connect and navigate scattered information.
 
@@
     \section{Conclusions}
+    We had fun with deciding the technology stack to use and the architecture structure.
+    We enjoyed the project freedom that allowed us to put in practice all the metholodogies
+    learnt from this course and all the others we had during the bachelor.
+
+    \section{References}
+    \begin{itemize}
+        \item \textit{ArtForSale} GitHub project public repository:\\
+              \url{https://github.com/JekxDevil/IR-ArtForSale}
+    \end{itemize}
 

### 2023-12-11 docs/report/submission.tex
feat: submission report architecture finished
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     \section{Introduction}
-    The Information Retrieval course project \textit{"ArtForSale"} aims to be a working prototype of an information
-    retrieval system for a specific task: to display for-sale artworks from art selling related websites
-    listed in Section \ref{sec:websites}.
+    The Information Retrieval course project \textit{"ArtForSale"} aims to be a working prototype of an
+    information retrieval system for a specific task: to display for-sale artworks from art selling related
+    websites listed in Section \ref{sec:websites}.
     The system has around $\approx 8,500$ indexed documents for searching, browsing and presented through a
     user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.
+    The source code repository of the project is linked in Section \ref{sec:references}.
 
@@
     \subsection{Features}
-    The course project requires 2 additional categorized features to be implemented besides the retrieval system:
+    The course project requires 2 additional categorized features to be implemented besides
+    the retrieval system:
     1 each from simple and complex group features.\\
@@
                   \item \textbf{Result presentation}:
-                        results should be presented in a tabular format so that many results could be seen at the same time.
+                        results should be presented in a tabular format so that many results could be
+                        seen at the same time.
                         Each table cell should contain appropriate information for your project.
@@
               \end{itemize}
-
         \item Complex
@@
                         In addition to the relevant search results pertaining to the user query,
-                        the user should also be suggested "similar" products based on, say, category, description,
-                        price etc. The ordering among the recommended items is not important.
+                        the user should also be suggested "similar" products based on, say,
+                        category, description, price etc.
+                        The ordering among the recommended items is not important.
                         However, you should mention how did you arrive at the recommendations.
@@
     and the filtering feature to filter them,
-    the \textbf{Results clustering} complex feature was tackled by allowing to
-    group the results into topics based on category tags.
+    the \textbf{Results clustering} complex feature was tackled by allowing to group the results
+    into topics based on category tags.
     Though, a negative filter to exclude documents based on categories was not added,
@@
               which offers \textbf{querying} and \textbf{browsing} capabilities.
-              Satisfies \textbf{short-term needs}.
+              It satisfies \textbf{short-term needs}.
         \item \textbf{Push}: system takes initiative and has good knowledge of what are the user's
@@
 
-    \newpage
-    \textbf{browser traces} collected in cookies for every search query user issues, part of recommender system.
+    The software components are: crawler, indexer, database, backend, frontend.\\
+    RESTful APIs are used as interface for commucation between indexer-backend and backend-frontend.
+    Communication between database-backend is encapsulated by Django,
+    while crawler-indexer needs to be run manually through CLI prompt and file writing.
 
     \subsection{Technology Stack}
+    Mandatory technologies to use for the project implementation: scrapy, pyterrier.
+    Here below is listed the tech stack used with a short description and motivation of choice.
 
     \subsubsection{Scrapy}
-    Scrapy, a Python framework for web crawling and scraping, is utilized in to initiate the crawling/scraping process for a specified set of artworks.
-The extracted data is subsequently channeled into a .json file.
+    Scrapy is a Python application framework for crawling web sites and extracting structured data.
+    It is used to initialize the crawling \& scraping process for a specified set of artworks.
+    Crawling process is further discussed in section \ref{sec:crawling}.
 
     \subsubsection{PyTerrier}
-    PyTerrier is a Python library that provides a high-level interface for the Terrier information retrieval system.
-In the provided code snippet, PyTerrier is used for building an information retrieval system to search and index documents.\newline
-    Our index.py file uses PyTerrier to create the index starting from the .json file
+    PyTerrier is a Python declarative platform for information retrieval experiments.
+    It uses the Java-based Terrier information retrieval platform internally to support indexing and
+    retrieval operations.
+    Indexer process is further discussed in section \ref{sec:indexing}.
 
     \subsubsection{Django \& SQLite}
-    The main part of the project has been carried using a Django based backend. The backend handles the main fetches from the frontend.
-    The backend is also the joint between the frontend and the index, making calls to a FASTApi that returns relevant documents given a query.\newline
-    To return to the frontend the main information about the documents, the backend iterates through a database in SQLite that contains the main information for each artwork
+    Django is a
+    FOSS\footnote{Free and Open Source}
+    high-level Python web framework for rapid development and clean, pragmatic design.
+    It takes care of much of the hassle of web development.\\
+    By default, the Django configuration uses SQLite as database,
+    which is the easiest choice of implementation already is included in Python.
+    Backend functionality and interaction with database is detailed in Sections
+    \ref{sec:backend}.
 
-    \subsubsection{Vue.js \& PrimeVue}
-    Finally, to develop the frontend, it has been used Vue.js, using the PrimeVue as UI library.
-Vue.js allows us to create a reactive and dynamic user interface, while PrimeVue provides us with a set of pre-built components and styles.
+    \subsubsection{Vue.js 3 \& PrimeVue}
+    The progressive javascript framework described as approachable, performant and versatile
+    for building web user interfaces.
+    It is an industry standard among the js component-based frameworks and it is used in courses
+    since the 2\textsuperscript{nd} year of the bachelor.\\
+    Together with PrimeVue, a complete UI suite for Vue.js, it elevates the web application with
+    customizable, feature-rich UI components.
+    %check responsivess
+    Frontend design specifics are in Sections \ref{sec:frontend}, \ref{sec:ui}, \ref{sec:ux}.\\
+
+    The search engine requirements are futher described, measured and discussed
+    in the Evaluation Section \ref{sec:evaluation}.
 
@@
     \section{Crawling}\label{sec:crawling}
+    Part of \textbf{Indexing Process}, regarding \textbf{Text Acquisition}, in which the system
+    identifies and stores documents for indexing.
+
     Harnesing (relatively) Bit Text Data characterized with the 5
@@
     easily indexed.
+    The extracted data is subsequently channeled into a .json file.
 
     \section{Indexing}\label{sec:indexing}
+    Part of \textbf{Indexing Process}, regarding \textbf{Text Transformation}, in which the system
+    transforms documents into index terms or features, \textbf{Index Creation}, where the
+    system takes index terms and creates data structures to support fast searching,
+    and \textbf{Ranking and Retrieval}, which uses query and index to generate a ranked list of docs.
+
     The Pyterrier platform supports indexing and retrieval operations by employing shallow
     NLP \footnote{Natural Language Processing}
-    techniques to enable computers to understand the meaning of natural language text.
+    techniques to enable computers to understand the meaning of natural language text.\\
+    Our index.py file uses PyTerrier to create the index starting from the .json file.
 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \section{Retrieval}
-    \subsection{Backend}
-    The backend relies on a SQLite database to store the main information about the documents, making possible to retrieve the relevant ones following a call to the index.\newline
-    Django serves as the foundational framework for constructing the primary structure, bringing with it a multitude of advantages such as rapid development, a robust and secure architecture, built-in administrative features, and a thriving community support ecosystem.\newline
+
+    \textbf{browser traces} collected in cookies for every search query user issues, part of recommender system.
+
+    \subsection{Backend}\label{sec:backend}
+    The backend relies on a SQLite database to store the main information about the documents,
+    making possible to retrieve the relevant ones following a call to the index.\newline
+    Django serves as the foundational framework for constructing the primary structure,
+    bringing with it a multitude of advantages such as rapid development, a robust and secure architecture,
+    built-in administrative features, and a thriving community support ecosystem.\newline
     The backend handles the two main fetches of the application:
     \begin{itemize}
-        \item /api/documents/get-documents/"query"/: This endpoint facilitates the retrieval of relevant documents based on a provided query string.
-        \item /api/recommendation/get-recommended/: This endpoint is tasked with retrieving recommended artworks.
-By inputting a set of tags, it conducts a search within the index, returning all pertinent documents associated with the specified criteria.
+        \item /api/documents/get-documents/"query"/:
+              This endpoint facilitates the retrieval of relevant documents based on a provided query string.
+        \item /api/recommendation/get-recommended/:
+              This endpoint is tasked with retrieving recommended artworks.
+              By inputting a set of tags, it conducts a search within the index,
+              returning all pertinent documents associated with the specified criteria.
     \end{itemize}
+    The backend handles the main fetches from the frontend.
+    The backend is also the joint between the frontend and the index,
+    making calls to a FASTApi that returns relevant documents given a query.
+    To return to the frontend the main information about the documents,
+    the backend iterates through a database in SQLite that contains the main information
+    for each artwork.
 
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \subsection{Frontend}
+    \subsection{Frontend}\label{sec:frontend}
+    Part of \textbf{Query and Retrieval Process}, regarding \textbf{User Interaction},
+    in which the system supports the creation of a query and display results.
+
+    transforms documents into index terms or features, and \textbf{Index Creation}, where the
+    system takes index terms and creates data structures to support fast searching.
+
     The frontend is the main part of the application, where all the features are implemented.\newline
@@
 
+    Vue.js allows us to create a reactive and dynamic user interface,
+
     \subsubsection{User Interface}\label{sec:ui}
@@
 
+    %\section{Feedback}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \section{Evaluation}
+    \section{Evaluation}\label{sec:evaluation}
+    Part of the \textbf{Query and Retrieval Process}, regarding \textbf{Evaluation}.\\
+
+    \textbf{Effectiveness}: quality of results. \textbf{Efficiency}: response time and throughput.
+
     System evaluation: Recall and precision paragraph
@@
     \subsection{User Evaluation}
+    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}
 
@@
 
-    \section{References}
+    \section{References}\label{sec:references}
     \begin{itemize}
-        \item \textit{ArtForSale} GitHub project public repository:\\
-              \url{https://github.com/JekxDevil/IR-ArtForSale}
+        \item \textit{ArtForSale} GitHub public repository: \url{https://github.com/JekxDevil/IR-ArtForSale}
+        \item Course slides on iCorsi: \url{https://www.icorsi.ch/course/view.php?id=16928}
+        \item \textit{Scrapy}: \url{https://docs.scrapy.org}
+        \item \textit{Pyterrier}: \url{https://pyterrier.readthedocs.io}
+        \item \textit{FastAPI}: \url{https://fastapi.tiangolo.com/}
+        \item \textit{Django}: \url{https://www.djangoproject.com/}
+        \item \textit{Vue.js 3}: \url{https://vuejs.org/}
+        \item \textit{PrimeVue}: \url{https://primevue.org/}
     \end{itemize}

### 2023-12-11 docs/report/submission.tex
feat: submission report crawler
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     \section{Crawling}\label{sec:crawling}
-    Part of \textbf{Indexing Process}, regarding \textbf{Text Acquisition}, in which the system
-    identifies and stores documents for indexing.
+    It is part of \textbf{Indexing Process}, regarding \textbf{Text Acquisition}, in which the system
+    identifies and stores documents for indexing.\\
+    The purporse is to harness (relatively) bit text data characterized with the 5
+    Vs\footnote{Volume, Variety, Velocity, Value, Veracity}
+    located in previous mentioned web sites regarding for sale art.
+    Among the 5 Vs, automating the Velocity attribute to keep track of the dynamic real-time data characterizing
+    the art selling market was not possible:
+    manual re-crawling of the spiders and inverted index re-creation is needed.
+    Crawling through Scrapy parses text that is unstructed to group it in well-structured documents,
+    allowing them to be easily indexed.
+    The structure of each documents is:
+    \vspace{-0.2cm}
+    \begin{itemize}
+        \setlength\itemsep{0.1em}
+        \item author
+        \item title
+        \item price
+        \item description
+        \item categories
+        \item image url reference
+        \item post url reference
+    \end{itemize}
 
-    Harnesing (relatively) Bit Text Data characterized with the 5
-    Vs \footnote{Volume, Variety, Velocity, Value, Veracity},
-    we lack automating the Velocity attribute since we need to rerun the spiders manually to update its
-    status on the inverted index.
-    Crawling parses text that is unstructed to group them in well-structured documents, allowing them to be
-    easily indexed.
-    The extracted data is subsequently channeled into a .json file.
+    The extracted data is subsequently channeled into a \textit{.json} file specified at start.
+    After all spiders have been run, every result is manually merged into the \textit{results.json} file.\\
+    Our sample volume is around $\approx 8,500$.
 
     \section{Indexing}\label{sec:indexing}
-    Part of \textbf{Indexing Process}, regarding \textbf{Text Transformation}, in which the system
-    transforms documents into index terms or features, \textbf{Index Creation}, where the
-    system takes index terms and creates data structures to support fast searching,
-    and \textbf{Ranking and Retrieval}, which uses query and index to generate a ranked list of docs.
-
+    It is part of \textbf{Indexing Process},
+    regarding \textbf{Text Transformation}, in which the system transforms documents into index terms,
+    \textbf{Index Creation}, where index terms are employed to create data structures to support fast searching,
+    and \textbf{Ranking and Retrieval}, which uses query and index to generate a ranked list of docs.\\
     The Pyterrier platform supports indexing and retrieval operations by employing shallow
     NLP \footnote{Natural Language Processing}
-    techniques to enable computers to understand the meaning of natural language text.\\
+    techniques.\\
+    The indexer served through a FastAPI server in \textit{crawler/index.py} file,
+    returns a ranked list of documents in descending order of relevance probability $p \in [0,1]$,
+    which is the optimal standard strategy justified by the
+    \textbf{Probability Ranking Principle} [Robertson 77].
+    The indexer creates the inverted index from the \textit{results.json} file containing the documents.
+    \newpage
+
     Our index.py file uses PyTerrier to create the index starting from the .json file.
+
+    Porter algorithmic Stemmer, stopword list, english word tokenisation is default in pyterrier.
+
+    Around x terms in the \textbf{lexicon}
+
+    BM25 model, similarity-based model with ranked retrieval including TF, IDF and sublinear TF transformation
+    to avoid single term dominance.
+
+    Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
+    at the end of each search to get more results.
+    This led to under-constrained query giving back not relevant results.
+    The reason was due to the fact that for our specific set of concerns, hence documents, the word
+    \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
+    \textbf{Zipf's Law}.
+
+    At start, every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
+    unsatisfying results: it seemed like only the first field (title) got indexed,
+    giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
+    Hence we decided to put every field into one big "blob" of text and then indexed that.
 
@@
     for each artwork.
+
+    recommender system
+    use-based information filtering and content-based information filtering
 
@@
     \subsection{User Evaluation}
-    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}
+    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.
 

### 2023-12-11 docs/report/submission.tex
feat: submission report indexer
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     The \textbf{Information Retrieval System} has capabilities limited to a
-    \textbf{TIS} \footnote{Text Information System}
+    \textbf{TIS}\footnote{Text Information System}
     with \textbf{Text retrieval}.\\
@@
     The structure of each documents is:
-    \vspace{-0.2cm}
+    \vspace{-0.1cm}
     \begin{itemize}
@@
     Our sample volume is around $\approx 8,500$.
+    To run crawling refer to project's \textit{README.md}.
 
@@
     The Pyterrier platform supports indexing and retrieval operations by employing shallow
-    NLP \footnote{Natural Language Processing}
+    NLP\footnote{Natural Language Processing}
     techniques.\\
@@
     \textbf{Probability Ranking Principle} [Robertson 77].
-    The indexer creates the inverted index from the \textit{results.json} file containing the documents.
-    \newpage
+    The indexer creates the inverted index from the \textit{results.json} file containing the scraped documents.
+    Characteristics of index:
+    \vspace{-0.1cm}
+    \begin{itemize}
+        \setlength\itemsep{0.1em}
+        \item Stemmer: Porter, algorithmic-basedd, Pyterrier's default
+        \item Stopword: Pyterrier's default
+        \item Tokenisation: English words, Pyterrier's default
+    \end{itemize}
 
-    Our index.py file uses PyTerrier to create the index starting from the .json file.
-
-    Porter algorithmic Stemmer, stopword list, english word tokenisation is default in pyterrier.
-
-    Around x terms in the \textbf{lexicon}
-
-    BM25 model, similarity-based model with ranked retrieval including TF, IDF and sublinear TF transformation
-    to avoid single term dominance.
-
-    Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
-    at the end of each search to get more results.
-    This led to under-constrained query giving back not relevant results.
-    The reason was due to the fact that for our specific set of concerns, hence documents, the word
-    \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
-    \textbf{Zipf's Law}.
-
-    At start, every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
-    unsatisfying results: it seemed like only the first field (title) got indexed,
-    giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
-    Hence we decided to put every field into one big "blob" of text and then indexed that.
+    The retrieval model is BM25: similarity-based model with ranked retrieval including
+    TF\footnote{Term Frequency},
+    IDF\footnote{Inverse Document Frequency}
+    and sublinear TF transformation to avoid single term dominance.
+    %Around x terms in the \textbf{lexicon}
+    To run the indexer refer to project's \textit{README.md}.
 
@@
 
+    Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
+    at the end of each search to get more results.
+    This led to under-constrained query giving back not relevant results.
+    The reason was due to the fact that for our specific set of concerns, hence documents, the word
+    \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
+    \textbf{Zipf's Law}.
+
+    At start, every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
+    unsatisfying results: it seemed like only the first field (title) got indexed,
+    giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
+    Hence we decided to put every field into one big "blob" of text and then indexed that.
+
     \textbf{Effectiveness}: quality of results. \textbf{Efficiency}: response time and throughput.

### 2023-12-11 docs/report/submission.tex
feat: submission report backend and frontend
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     Shown results are sorted in descending order of relevance from left to right in the tabular view.\\
-    Implementation details of features are on Architecture Section \ref{sec:architecture}.\\
+    Implementation details are on Architecture, Recommender and Filtering Sections
+    \ref{sec:architecture}, \ref{sec:recommender}, \ref{sec:filtering}.\\
     Moreover, by exploiting the automatic recommandation feature implemented using category tags
@@
     After all spiders have been run, every result is manually merged into the \textit{results.json} file.\\
-    Our sample volume is around $\approx 8,500$.
+    Our sample volume is around $\approx 8,500$ entries.
     To run crawling refer to project's \textit{README.md}.
@@
 
-    \textbf{browser traces} collected in cookies for every search query user issues, part of recommender system.
-
     \subsection{Backend}\label{sec:backend}
     The backend relies on a SQLite database to store the main information about the documents,
-    making possible to retrieve the relevant ones following a call to the index.\newline
-    Django serves as the foundational framework for constructing the primary structure,
-    bringing with it a multitude of advantages such as rapid development, a robust and secure architecture,
-    built-in administrative features, and a thriving community support ecosystem.\newline
+    making it possible to retrieve the relevant ones following a call to the index.\newline
     The backend handles the two main fetches of the application:
+
     \begin{itemize}
-        \item /api/documents/get-documents/"query"/:
-              This endpoint facilitates the retrieval of relevant documents based on a provided query string.
-        \item /api/recommendation/get-recommended/:
-              This endpoint is tasked with retrieving recommended artworks.
+        \item \textit{GET /api/documents/get-documents/\underline{query}/}:
+              Endpoint facilitating the retrieval of relevant documents based on a provided \underline{query} string.
+        \item \textit{GET /api/recommendation/get-recommended/}:
+              Endpoint tasked with retrieving recommended artworks.
               By inputting a set of tags, it conducts a search within the index,
-              returning all pertinent documents associated with the specified criteria.
+              returning all pertinent documents associated with the specified category tags.
     \end{itemize}
-    The backend handles the main fetches from the frontend.
-    The backend is also the joint between the frontend and the index,
-    making calls to a FASTApi that returns relevant documents given a query.
-    To return to the frontend the main information about the documents,
-    the backend iterates through a database in SQLite that contains the main information
-    for each artwork.
 
-    recommender system
-    use-based information filtering and content-based information filtering
+    The backend is the joint between the frontend and the indexer.
+    It routes fetch request and, given a query, it returns the list of relevant documents with its main information
+    by iterating through the database containing it for each artwork.
+
+    \subsubsection{Automatic recommendation}\label{sec:recommender}
+    The 2\textsuperscript{nd} API call is used to implement the \textit{recommender system}:
+    the frontend keeps track of the categories as \textbf{browser traces} from the results given by user's queries.
+    Then, the indexer receives such categories as query and give back a set of documents to the backend.
+    This set is populated with its information stored in the database and it is finally given back to the frontend in
+    the suggestions carousels.
+    Essentially, once all the artworks related to the query have been retrieved,
+    the frontend extracts from all these artworks the related tags,
+    it chooses the ones with the higher frequency, fetches result using the API call and
+    shows a maximum of 5 results related to each tag in a moving carousel
+    It is a \textbf{Content-Based Information Filtering}:
+    recommendation in such dynamic collection is individual to users based on interest and preferences inferred from
+    previous user pseudo feedback, hence assuming top retrieved documents are relevant.
+    At the end of each section the recommendations tags are cleaned i.e. page reload.
+
+    % photo of carousel
+    \begin{figure}[H]
+        \centering
+        \caption{Automatic Recommendation - Carousel}
+        \label{fig:carousel}
+        \includegraphics[width=0.3\textwidth, trim={0cm 0cm 0cm 0cm}]{figures/recommendation-carousel.jpeg}
+    \end{figure}
 
     \subsection{Frontend}\label{sec:frontend}
-    Part of \textbf{Query and Retrieval Process}, regarding \textbf{User Interaction},
-    in which the system supports the creation of a query and display results.
+    Part of \textbf{Query and Retrieval Process},
+    regarding \textbf{User Interaction}, in which the system supports the creation of a query and display results.\\
+    The frontend is the main part of the application, where all the features are implemented.
+    For the interface, it has been chosen a simple layout, consisting of only a search bar and a search button.
+    Once the user performs the search, the aspect of the page changes, adding new components:
 
-    transforms documents into index terms or features, and \textbf{Index Creation}, where the
-    system takes index terms and creates data structures to support fast searching.
+    \begin{figure}[H]
+        \centering
+        \caption{UI of the \textit{Art For Sale} project}
+        \label{fig:carousel}
+        \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 2cm}, clip]{figures/ui.jpeg}
+    \end{figure}
 
-    The frontend is the main part of the application, where all the features are implemented.\newline
-    For the interface, it has been chosen a simple layout, consisting of only a search-bar and a search button.
-Once the user performs the search, the aspect of the page changes, adding new components.
-We will examine each of them:
     \begin{itemize}
-        \item First, under the search-bar will appear a new set of control to filter the obtained results according to four main characteristics: site of origin, minimum price, maximum price and tag.
-        \item Second, there will be shown some carousels for the recommended results based on the most frequents tags of the resulted artworks.
-Essentially, once all the artworks related to the query have been retrieved, the frontend extracts from all these artworks the related tags, it chooses the ones with the higher frequency and, using the /api/recommendation/get-recommended/ fetch, it shows a maximum of 5 results related to each tag in a moving carousel
-        \item Finally, the artworks retrieved from the query are displayed in a card-like style, showing an insight of the artwork, the author, the title, the price, a short description and the main tags, with a Visit button that will bring the user to the page of that artwork in the original site
+        \item \underline{Filter selectors}: under the search bar there are filter selectors to control the obtained results
+              according to 4 main characteristics:
+              site of origin, minimum price, maximum price and category tag.
+        \item \underline{Recommended Carousel}:
+              At the right side of the page, the recommended carousel suggests results based on the most frequent tags
+              of the resulted artworks.
+              It shows a maximum of 5 results related to each tag in a moving carousel.
+        \item \underline{Document tabular view}: retrieved artworks from the query are displayed in card components,
+              following a tabular view as requested by the simple feature implemented.
+              The card shows an insight of artwork image, author, title, price, short description and main tags,
+              with a \textit{"Visit"} button that will bring the user to the page of that artwork in the original website.
     \end{itemize}
-
-    Vue.js allows us to create a reactive and dynamic user interface,
 
@@
 
+    Jacobs heuristics respected
+    UI has been layed out following Jakob's 10 usability heuristics as much as possible:
+
     Emotional design: key in Apple, Google alike
-
-    Jacobs heuristics respected
 
@@
 
-    %\section{Feedback}
+    \subsubsection{Filtering}\label{sec:filtering}
+    The filtering features is implemented frontend side:
+    the filter string representation is checked in every documents, the ones which have it are still shown,
+    otherwise it is hidden.
+    If no filter is selected, then it simply shows all the results from the query.
+
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-    SUS includes pia, quote are designers users too?
+    SUS includes someone normal not studying informatics, quote are designers users too?
+
+    \begin{figure}[H]
+        \centering
+        \caption{Loading animation while retrieving documents}
+        \label{fig:carousel}
+        \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 0cm}, clip]{figures/loading.jpeg}
+    \end{figure}
 

### 2023-12-11 docs/report/submission.tex
feat: submission report frontend
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     The frontend is the main part of the application, where all the features are implemented.
-    For the interface, it has been chosen a simple layout, consisting of only a search bar and a search button.
+    For the interface, it has been chosen a simple layout shown in Figure \ref{fig:ui},
+    consisting of only a search bar and a search button.
     Once the user performs the search, the aspect of the page changes, adding new components:
@@
         \caption{UI of the \textit{Art For Sale} project}
-        \label{fig:carousel}
+        \label{fig:ui}
         \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 2cm}, clip]{figures/ui.jpeg}
@@
     \subsubsection{User Interface}\label{sec:ui}
-
-    Jacobs heuristics respected
-    UI has been layed out following Jakob's 10 usability heuristics as much as possible:
-
-    Emotional design: key in Apple, Google alike
-
-    standard filtering system
+    UI has been layed out following Jakob's 10 usability heuristics as much as possible, particularly:
+    aesthetic and minimalist design, visibility of system status and consistency and standards.\\
+    Norman's Emotional Design guidelines have been followed to obtain a UI gradient effect and minimalism similar
+    to what is the user experience in Apple products, so users will feel confortable using it.
 
     \subsubsection{Filtering}\label{sec:filtering}
-    The filtering features is implemented frontend side:
-    the filter string representation is checked in every documents, the ones which have it are still shown,
-    otherwise it is hidden.
+    The filtering features is implemented frontend side.
     If no filter is selected, then it simply shows all the results from the query.
+    Otherwise, it checks:
+    \begin{itemize}
+        \setlength\itemsep{0.1em}
+        \item price value range: check if the document value is between the min and max inserted
+        \item web sites: check if the document origin url contains the selected website(s)
+        \item category: the UI allows only to select a category from the ones already present in the result of your query
+    \end{itemize}
 

### 2023-12-11 docs/report/submission.tex
feat: start user evaluation
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     Part of the \textbf{Query and Retrieval Process}, regarding \textbf{Evaluation}.\\
-
+    \textbf{Effectiveness}: quality of results.
     Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
@@
     giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
-    Hence we decided to put every field into one big "blob" of text and then indexed that.
-
-    \textbf{Effectiveness}: quality of results. \textbf{Efficiency}: response time and throughput.
-
-    System evaluation: Recall and precision paragraph
+    Hence we decided to put every field into one big "blob" of text and then indexed that.\\
+    \textbf{Efficiency}: response time and throughput.
+    Since there is no pagination of results, all the list of relevant documents is sent and shown at once
+    in the single page.
+    This can lead to queries that give back hundred of documents and the response time to render them is high
+    and has been partially leverage in the UX by adding a loader animation for retrieval,
+    shown in Figure \ref{fig:loader}.
 
     \subsection{User Evaluation}
-    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.
-
-    SUS includes someone normal not studying informatics, quote are designers users too?
+    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.\\
+    The conducted SUS modules are in \textit{docs/user-evaluation.pdf}.
+    After the development, we have conduct an user evaluation on 5 different users using the SUS questionnaire.
+    The SUS questionnaire is a 10-item questionnaire that measures the usability of a system.
+    Each question is rated on a 5-point Likert scale, from strongly disagree to strongly agree.
+    At the end of the questionnaire, we can compute the SUS score, which is a number between 0 and 100
+    that indicates how usable the system is.
+    We asked 5 users to use the system and fill the SUS questionnaire.
+    While using the system we asked them to perform some tasks, such as searching for artworks,
+    check the recommendations and use the filters.
+    Sentiment analysis: all the users found the system intuitive and well-structured,
+    without needing particular help to perform the various tasks.
+    Once computed, we have obtained a 91.5\% SUS score.
+    Given the results of the SUS questionnaire, we can say that the system is definitely usable
+    and that the users are satisfied with it.
 
@@
         \caption{Loading animation while retrieving documents}
-        \label{fig:carousel}
+        \label{fig:loader}
         \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 0cm}, clip]{figures/loading.jpeg}
@@
 
-    \subsubsection{User Experience}\label{sec:ux}
-    Sentiment analysis
-
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    %\section{Running information}
     \section{Limitations and Future Improvements}
@@
     \section{Conclusions}
+    The project results is overall satifactory.
+    We went for a couple iterations cycles to develop the whole stack and choosing the right tools aka frameworks
+    allowed us to focus on the final result rather than non relevant technicalities.
     We had fun with deciding the technology stack to use and the architecture structure.

### 2023-12-11 crawler/index.py
build: devops for project dependencies handling
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@ -40,7 +40,7 @@ app.add_middleware(
 def search(query: str):
     print(query)
     reverse_index = pt.IndexFactory.of('./index_total')
-    tf_idf = pt.BatchRetrieve(reverse_index, wmodel="TF_IDF")
+    tf_idf = pt.BatchRetrieve(reverse_index, wmodel="BM25")
     output = tf_idf.search(query)
     return output.to_dict()
 

### 2023-12-11 docs/report/submission.tex
Modified report

@@
     The system has around $\approx 8,500$ indexed documents for searching, browsing and presented through a
-    user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}, \ref{sec:ux}.
+    user-friendly and intuitive interface, further details in UI/UX Section \ref{sec:ui}.
     The source code repository of the project is linked in Section \ref{sec:references}.
+
+    \subsection{Dowload}
+    The complete code exceeded the size allowed by iCorsi. For this reason, the repository can be found at \url{https://github.com/JekxDevil/IR-ArtForSale}
 

### 2023-12-11 docs/report/submission.tex
feat: submission report finished
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

@@
     \subsection{Dowload}
-    The complete code exceeded the size allowed by iCorsi. For this reason, the repository can be found at \url{https://github.com/JekxDevil/IR-ArtForSale}
+    The complete code exceeded the size allowed by iCorsi.
+    For this reason, the repository can be found at
+    \url{https://github.com/JekxDevil/IR-ArtForSale}.
+    The release at submission is \textit{submission} with tag \textit{v1.0.0} and commit hash
+    \textit{asdfasdfasdf}.
 
@@
     Part of the \textbf{Query and Retrieval Process}, regarding \textbf{Evaluation}.\\
-    \textbf{Effectiveness}: quality of results.
-    Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
-    at the end of each search to get more results.
+    \newline
+    \textbf{Effectiveness}: quality of results.\\
+    An attempt to improve effectiveness was employing of \textbf{query expansion},
+    tested by always adding the \textit{art} keywork at the end of each search to get more results.
     This led to under-constrained query giving back not relevant results.
@@
     \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
-    \textbf{Zipf's Law}.
-
-    At start, every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
+    \textbf{Zipf's Law}.\\
+    A change to improve effectiveness was done when we noticed that at start,
+    every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
     unsatisfying results: it seemed like only the first field (title) got indexed,
-    giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
+    giving an \textbf{over-constrained query} feeling where
+    either no documents or no relevant ones were returned,
     Hence we decided to put every field into one big "blob" of text and then indexed that.\\
-    \textbf{Efficiency}: response time and throughput.
-    Since there is no pagination of results, all the list of relevant documents is sent and shown at once
-    in the single page.
-    This can lead to queries that give back hundred of documents and the response time to render them is high
-    and has been partially leverage in the UX by adding a loader animation for retrieval,
-    shown in Figure \ref{fig:loader}.
-
-    \subsection{User Evaluation}
-    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.\\
-    The conducted SUS modules are in \textit{docs/user-evaluation.pdf}.
-    After the development, we have conduct an user evaluation on 5 different users using the SUS questionnaire.
-    The SUS questionnaire is a 10-item questionnaire that measures the usability of a system.
-    Each question is rated on a 5-point Likert scale, from strongly disagree to strongly agree.
-    At the end of the questionnaire, we can compute the SUS score, which is a number between 0 and 100
-    that indicates how usable the system is.
-    We asked 5 users to use the system and fill the SUS questionnaire.
-    While using the system we asked them to perform some tasks, such as searching for artworks,
-    check the recommendations and use the filters.
-    Sentiment analysis: all the users found the system intuitive and well-structured,
-    without needing particular help to perform the various tasks.
-    Once computed, we have obtained a 91.5\% SUS score.
-    Given the results of the SUS questionnaire, we can say that the system is definitely usable
-    and that the users are satisfied with it.
+    \newline
+    \textbf{Efficiency}: response time and throughput.\\
+    Since there is no pagination of results, all the list of relevant documents is sent
+    and shown at once in the single page.
+    This can lead to queries that give back hundred of documents
+    and the response time to render them is high and has been partially leveraged
+    in the UX by adding a loader animation for retrieval as shown in Figure \ref{fig:loader}.
 
@@
     \end{figure}
+
+    \subsection{User Evaluation}
+    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.\\
+    The conducted SUS modules are in \textit{docs/user-evaluation.pdf}.
+    After the development, we conducted an user evaluation on 5 different users
+    using the \textbf{SUS questionnaire}.
+    The SUS questionnaire is a 10-item questionnaire that measures the usability of a system.
+    Each question is rated on a 5-point Likert scale, from strongly disagree to strongly agree.
+    At the end of the questionnaire, we can compute the SUS score, which is a number
+    between 0 and 100 that indicates how usable the system is.
+    We asked 5 users to use the system, fill the SUS questionnaire and signing it.
+    While using the system we asked them to perform the following tasks:
+    \begin{itemize}
+        \setlength\itemsep{0.1em}
+        \item familiaze for 10 seconds with the platform
+        \item search for an artwork
+        \item try out the filters
+        \item check the suggested recommendations
+    \end{itemize}
+    The first 3 SUS forms were done a week before the submission, hence we had the time to
+    implement the suggested enhancements during the last sprint iteration of development:
+    \begin{itemize}
+        \setlength\itemsep{0.1em}
+        \item put the recommendation carousel on a side
+        \item reset of filters after each search
+        \item adjust card size
+        \item add a spinner during loading of results since it is not intuitive it is loading them
+        \item add enter event listener to search bar to directly query the system
+    \end{itemize}
+
+    \underline{Sentiment analysis}: all users found the system intuitive and well-structured,
+    without needing particular help to perform the various tasks.
+    Once computed, we have obtained a 91.5\% SUS score.
+    Given the results of the SUS questionnaire, we can say that the system is definitely usable
+    and that the users are satisfied with it.
 
